---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup


The Behavorial Risk Factor Surveilance System (BRFSS) has been around since 1984 and is a phone survey conducted monthly in the fifty US states and annually in US territories. This analysis will be taking a look at the BRFSS data collected between 2013-01-01 and 2014-03-13, from all fifty states as well as the District of Columbia, Guam and Puerto Rico, analyzing for any interesting trends or correlations.

### Load packages

```{r load-packages, message = FALSE}
ifelse(!require(tidyverse), install.packages("tidyverse"), library(tidyverse))
ifelse(!require(pander), install.packages("tidyverse"), library(pander))
ifelse(!require(lubridate), install.package("lubridate"), library(lubridate))
```

### Load data

```{r load-data}
load("brfss2013.RData")
```



* * *

## Part 1: Data


The BRFSS data is collected via a phone survey. The phone survey can be conducted either via a landline or a cell phone. In the case of a landline, the surveyer collects data from a randomly selected adult in the household. In the case of a cell phone call, the data is collected from an adult with a cell phone number registered to a private residence or a college dwelling.

Data is collected by each of the fifty states in the United States (US) and participating US territories independently and reported up to the Centers for Disease Control (CDC) on a 1-3 month basis.

Based on the codebook, the main survey consists of 16 sections:

- record info (for identificaton purposes)
- health status
- healthy days - health related quality of life
- health care access
- inadequate sleep
- hypertension awareness
- cholesterol awareness
- chronic health conditions
- demographics
- tobacco use
- alcohol consumtion
- fruits and vegetables
- exercise
- arthritis burden
- seatbelt use
- immunization
- HIV/AIDS

In addition, there are 22 optional modules as well as other demographic variables.

* * *

## Part 2: Research questions

**Research quesion 1:**

**Research quesion 2:**

**Research quesion 3:**


* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

**Research quesion 1:**

```{r}

```



**Research quesion 2:**

```{r}

```



**Research quesion 3:**

```{r}

```


## Addendum

### Computer Info
```{r session}
sessionInfo()
```